TacticToe: Learning the Game of Tactics

### 2018-02-10 tactictoe_jv.tex
minor

\section{Case Study}
In this section, we compare \tactictoe proof script with human proof script.

@@

%A first successful use of orthogonalization techniques for theorems appeared in
%a work on lemma mining~\cite{ckju-jsc15} in \hollight. Theorems were mined
%from
%proofs recorded at the kernel level. Because the number of recorded lemmas was
%in millions, page ranking techniques was used as a filter to extract
%``useful''
%lemmas.

\todoi{Is copied and modified}
We proposed a new proof assistant automation technique which combines
tactic-based proof search with machine learning tactic prediction
Its implementation,
\tactictoe, achieves an overall performance of 66.4\% theorems on 7164
theorems
of the \holfour standard library surpassing \eprover with
auto-schedule. Its
effectiveness is especially visible on
theories which use inductive data structures, specialized decision procedures,
and custom built simplification sets.
Thanks to the learning abilities of \tactictoe, the generated proof scripts
usually reveal the high-level structure of the proof. %For these reasons,
We therefore believe that predicting ITP tactics based on the current goal
features is a very reasonable approach to automatically guiding proof search,
and that accurate predictions can be obtained by learning from the knowledge
available in today's large formal proof corpora.
%And it seems to get us
%closer to the way how humans learn to do theorem proving.

There is plenty of future work in the directions opened here.

To improve the quality of the predicted tactics,
we would like to predict other type of arguments independently, as it was done
for theorems. In this direction, the most interesting type of arguments to
predict next are terms as they are ubiquitous in tactics. Further along the way,
we would like to be to able to create new tactics not only by changing their
arguments but also by programming it with any construction available in a
programming language such as \sml.

There is still something to be gain by having a better guidance for the search.
That is why se also want to experiment with stronger machine learning algorithm
such as deep neural networks as a model for the policy and evaluation in MCTS.
This quality of this model could be enhanced by additional data augmentation by
training and testing existing and synthesized tactics.
Another possible way to guide the proof search is by conjecturing intermediate
steps \cite{}, allowing to prove a difficult theorem by decomposing it into
multiple easy steps.

%Future work:
%  Promising techniques that could not be evaluated.
%  + Orthogonalization of theorems~\cite{ckju-jsc15}.
%  + Try harder and smarted on term predictions.
%  \cite{conjecturing}
%  + Self-learning.
%+ MCTS was presented in manner that we only did the first step of
%reinforcement
%learning. CurrentPolicy becomes PriorPolicy.
% + More training than just orthogonalization of tactics.

>>>>

\section{Case Study}\todo{comment on the case study}
In this section, we compare \tactictoe proof script with human proof script.

@@

We proposed a new proof assistant automation technique which combines
tactic-based proof search with machine learning prediction
Its implementation, \tactictoe, achieves an overall performance of 66.4\% 
theorems on 7164 theorems of the \holfour standard library surpassing \eprover 
with auto-schedule. Its
effectiveness is especially visible on
theories which use inductive data structures, specialized decision procedures,
and custom built simplification sets.
Thanks to the learning abilities of \tactictoe, the generated proof scripts
usually reveal the high-level structure of the proof. %For these reasons,
We therefore believe that predicting ITP tactics based on the current goal
features is a very reasonable approach to automatically guiding proof search,
and that accurate predictions can be obtained by learning from the knowledge
available in today's large formal proof corpora.

To improve the quality of the predicted tactics,
we would like to predict other type of arguments independently, as it was done
for theorems. In this direction, the most interesting arguments to
predict next are terms as they are ubiquitous in tactics. Further along the way,
new tactics could be created by programming them with any construction 
available in \sml. There is also something to be gain by 
having a better guidance for the search.
That is why se also want to experiment with stronger machine learning algorithm
such as deep neural networks as a model for the policy and evaluation in MCTS.
This quality of this model could be enhanced by additional data augmentation by
training and testing existing and synthesized tactics.
Conjecturing suitable intermediate steps could also allow \tactictoe to solve 
a problem which requires a long proof by decomposing it into multiple easy 
steps.
